---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# anidb

<!-- badges: start -->
<!-- badges: end -->

`anidb` is an R-package that returns information from the anime database at [AniDB](https://anidb.net). **You should not use this package to request the same dataset multiple times on a single day or flood it with requests -- otherwise you can get banned by the AniDB administrators.** If using `Rmd`, you should add `cache = TRUE` in chunks. For interactive use, `anidb` employs a simple caching mechanism.

## Installation

You can install the development version of anidb from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("emitanaka/anidb")
```

## Example

```{r, include = FALSE}
knitr::opts_chunk$set(cache.path = "cache/")
```


```{r setup}
library(anidb)
```

Get all IDs with anime titles that has an approximate matching with "one piece" ignoring case:

```{r}
aids <- anime_id(title = "one piece")
```

You can check the official titles of these anime IDs:

```{r}
official_title(aids)
```



```{r anime-info, cache = TRUE}
onepiece <- anime_info(aids)
```
```{r}
head(onepiece)
```

```{r}
library(ggplot2)
ggplot(onepiece, aes(start_date, rating)) + 
  geom_point()
```


